%-------------------------
% Resume in Latex
% Author : Phillip Ring
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeCoursework}[1]{
  \item\small{
    \textbf{Relevant Coursework:} #1 \vspace{-2pt}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Phillip Ring} \\ \vspace{1pt}
    \href{mailto:x@x.com}{\underline{phillip.roy.ring@gmail.com}} $|$ 
    \href{https://linkedin.com/in/ring-phillip}{\underline{linkedin.com/in/ring-phillip}} $|$
    \href{https://github.com/philwing100}{\underline{github.com/philwing100}} $|$ \small 512-765-3585
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Texas at Austin}{Aug. 2025 -- May 2027}
      {Master of Science in Computer Science}{Austin, TX}
    \resumeSubheading
      {University of Texas at Tyler}{Sep. 2021 -- May 2025}
      {Bachelor of Science in Computer Science}{Tyler, TX}
    \resumeCoursework{Parallel Systems, Advanced Operating Systems, Computer Architecture, Unix Shell Programming, Deep Learning}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
\resumeSubheading
  {Software Engineer}{July 2025 -- Present}
  {Heartland National TB Center - Full Time}{San Antonio, TX}
  \resumeItemListStart
  \resumeItem{Translated medical requirements from doctors and nurses into technical solutions.}
    \resumeItem{Used C\#, JS and MSSQL to create medical consultation database receiving \textbf{1600} consultations per year.}
    \resumeItem{Conducted meetings with IT Operations Manager and Director of IT Infrastructure to secure cloud infrastructure.}
    \resumeItem{Built REST endpoints in C\# .NET to power data exports of consultation data as graphs and charts for staff.}
  \resumeItemListEnd

\resumeSubheading
  {Software Engineer Intern}{Sep. 2024 -- Dec. 2024}
  {zdSCADA - Part Time}{Tyler, TX}
  \resumeItemListStart
    \resumeItem{Built full stack services using C\# .NET, Vue.js, and MSSQL database to support industrial SCADA systems.}
        \resumeItem{Saved \textbf{80} hours per year by automating the invoice generation pipeline for the accounting team.}
    \resumeItem{Implemented a backend logging solution that exposed critical defects early, reducing production incidents.}
    \resumeItem{Utilized Azure DevOps for branch management, tracking user stories, and streamlining pull request workflows.}
  \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
    \resumeProjectHeading
          {\textbf{GPU-Accelerated K-Means Optimization} $|$ \emph{C++, Cuda, Thrust}}{ Sep. 2025 -- Oct. 2025}
          \resumeItemListStart
           \resumeItem{Implemented three GPU-parallel K-Means variants using CUDA and Thrust.}
            \resumeItem{Achieved \textbf{17×} faster iteration time than a sequential CPU baseline via kernel and memory optimizations.}
            \resumeItem{Benchmarked scalability across dataset sizes, analyzing bandwidth limits and atomic contention.}
          \resumeItemListEnd
    \resumeProjectHeading
          {\textbf{Parallel Prefix Scan and Barriers UTA Project} $|$ \emph{C++, Python}}{ Aug. 2025 -- Sep. 2025}
          \resumeItemListStart
            \resumeItem{Implemented a work efficient asynchronous prefix scan using POSIX threads.}
            \resumeItem{Built a custom reentrant barrier using localsense spinlocks, achieving \textbf{223\%} speedup over pthread barriers.}
            \resumeItem{Identified scalability bottlenecks at high thread counts and optimized workload distribution.}
            \resumeItem{Wrote Python scripts for reproducible experiments and statistical analysis.}
          \resumeItemListEnd
        \resumeProjectHeading
          {\textbf{Two Phase Commit} $|$ \emph{Rust}}{Sep. 2024 -- Dec. 2024}
          \resumeItemListStart
            \resumeItem{Built a distributed two-phase commit simulator in Rust with concurrent coordinator and participant nodes.}
            \resumeItem{Simulated probabilistic failures using bidirectional channels and asynchronous messaging.}
            \resumeItem{Improved coordinator throughput by replacing blocking waits with non-blocking polling on the critical path.}
            \resumeItem{Used Rust ownership and concurrency guarantees to prevent deadlocks and unsafe shutdowns.}
          \resumeItemListEnd
          \resumeProjectHeading
          {\textbf{Transformer-Based Autonomous Driving Planner} $|$ \emph{Pytorch}}{Fall 2025}
          \resumeItemListStart
        \resumeItem{Built an end-to-end autonomous driving planner in PyTorch to predict vehicle trajectories from sensor inputs.}
        \resumeItem{Implemented and compared MLP, CNN, and Transformer-based planners with cross-attention over learned queries.}
        \resumeItem{Designed a modular training pipeline with custom datasets, losses, metrics, and checkpointing.}
        \resumeItem{Met strict trajectory error thresholds and validated closed-loop driving performance in SuperTuxKart simulation.}
          \resumeItemListEnd
          \resumeProjectHeading
          {\textbf{High-Frequency Order Matching Engine} $|$ \emph{C++}}{2024}
          \resumeItemListStart
            \resumeItem{Built a concurrent order matching engine in C++ using a producer-consumer architecture with a simulated exchange thread generating randomized multi-symbol market orders.}
            \resumeItem{Designed per-symbol order books with a sorted \texttt{std::map} for O(log N) price-level insertion and O(1) best bid/ask crossing, and an \texttt{unordered\_map} for O(1) order cancellation by ID.}
            \resumeItem{Implemented a thread-safe order stream using mutex and condition variables, enabling lock-safe handoff between order generation and matching without busy-waiting.}
            \resumeItem{Benchmarked throughput using \texttt{std::atomic} counters, achieving over \textbf{250k} orders per second while tracking match rate and RSS memory footprint.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C/C++, Python, C\#, SQL (Postgres, mySQL, T-SQL), Js, BASH} \\
     \textbf{Technologies}{: Pytorch, Matplotlib, Docker, .NET, Vue.js, Node.js, Playwright, WSL, Ubuntu} \\
     \textbf{Developer Tools}{: Git, Github Actions, Linux, Generative AI, VS Code, Valgrind,  Agile Methodology} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
